### 2019-12-21 Statistical Methods/07_hypothesis-testing.rmd
statistical methods, ch7 wrap-up
statistical methods, ch7 wrap-up

@@

@@

@@

@@

@@

>>>>

trim <- .2; alpha <- 0.05; h0 <- 45; n <- length(x)
xbar <- mean(x, tr = trim)
sw <- 1.73

g <- floor( trim * n )
df <- n - 2*g - 1

crit <- qt(1 - alpha/2, df)

score <- ( 1 - 2*trim ) * (xbar - h0) / sw * sqrt(n)

ifelse(abs(score) > crit, "Reject", "Fail to reject")
```

@@

```{r, echo = T}
xbar <- 5.1; sw <- 7; n <- 25
alpha <- 0.01; h0 <- 4.8; trim <- .2

g <- floor(n*trim)

df <- n - 2*g - 1

crit <- qt(1 - alpha/2, df)

score <- (1 - 2*trim) * (xbar - h0) / sw * sqrt(n)

ifelse(abs(score) > crit, "Reject", "Fail to reject")
```

@@

```{r, echo = T}
flag=which(ToothGrowth[,3]==0.5)
trimci(ToothGrowth[flag,1],null.value=8,tr=0)
```

@@

```{r, echo = T}
trimci(ToothGrowth[flag,1],tr=0.2,null.value=8)
```

@@

```{r, echo = T}
akerd(ToothGrowth[flag,1])
```

@@

```{r, echo = T}
id=which(ToothGrowth[,3]==0.5)
momci(ToothGrowth[id,1],null.value=8)
```
